### 2023-11-08 thesis/sections/5-grounding.tex
results

% SD: Very good If I understand this right this would be a case where the generated description describes another object better than the target and a human would identify that. So it is like false negatives in describing. Perhaps use another term for this: referring to a distractor? (since you are not measuring hwo individually the description fitts a distractor but only if the entire description could perfectly fit a distractor)
% DK: exactly. I added false negatives. But I would like to keep accuracy in the name, since that is what it is. maybe better distractor accuracy? (QUESTION)
With the \textbf{non-target accuracy}, we identify if the model described another object, which is not the target image.
This is basically an inverted accuracy score; the lower the score, the better the model fares.
By this it measures the false negative generated captions.
For this we generated captions for all the non-target objects and distractors in the images using the GRE-algorithm.
If the generated description of the model describes an object that is not the target object, it gets assigned 100\%.
If not, independently of describing the target object, no object, or one of the objects insufficiently, it gets assigned 0\%.
Using this measure, we can get an overview if the model's problem lies in extracting and relating attributes or in understanding which of the presented objects is the target object.

>>>>

% SD: Very good If I understand this right this would be a case where the generated description describes another object better than the target and a human would identify that. So it is like false negatives in describing. Perhaps use another term for this: referring to a distractor? (since you are not measuring hwo individually the description fitts a distractor but only if the entire description could perfectly fit a distractor)
% DK: exactly. I added false negatives. But I would like to keep accuracy in the name, since that is what it is. maybe better distractor accuracy? (QUESTION)
With the \textbf{non-target accuracy}, we identify if the model described another object, which is not the target image.
This is basically an inverted accuracy score; the lower the score, the better the model fares.
By this it measures the false negative generated captions.
For this, referring generations are generated for all the non-target objects and distractors in the images using the GRE-algorithm.
Importantly to notice is that the referring expressions may not uniquely identify a distractor, since multiple distractors with the same shape, color and size are allowed.
If the generated description of the model describes an object that is not the target object, it gets assigned 100\%.
If not, independently of describing the target object, no object, or one of the objects insufficiently, it gets assigned 0\%.
Using this measure, we can get an overview if the model's problem lies in extracting and relating attributes or in understanding which of the presented objects is the target object.
